\textbf{SPECFEM3D}\\ \textbf{Cartesian}\\ \textbf{User Manual}

### 2023-06-02 doc/USER_MANUAL/copyright_and_version.tex

version 4.0, December 2022:
Rafael Almada, Jean-Paul Ampuero, Etienne Bachmann, Kangchen Bai, Stephen Beller, Jordan Bishop, Alexis Bottero,
Emanuele Casarotti, Clement Durochat, Rene Gassmoeller, Hom Nath Gharti, Leopold Grinberg, Aakash Gupta,
Foivos Karakostas, Dimitri Komatitsch, Qinya Liu, Geordie McBain, Ryan Modrak, Vadim Monteiller, Masaru Nagaso, Elif Oral,
Daniel Peter, Elliott Sales de Andrade,  James Smith, Carl Tape, Eduardo Valero Cano, Huihui Weng, Zhinan Xie:
various code improvements (fault solver, FK/DSM/AxiSEM coupling, gravity perturbations, energy integrals);
inverse problem module; parallel heuristic mesh decomposer; ADIOS2 file I/O support;
ASDF seismogram output; HIP GPU support.\newline

>>>>

version 4.0, March 2023:
Rafael Almada, Jean-Paul Ampuero, Etienne Bachmann, Kangchen Bai, Stephen Beller, Jordan Bishop, Alexis Bottero,
Emanuele Casarotti, Clement Durochat, Rene Gassmoeller, Hom Nath Gharti, Leopold Grinberg, Aakash Gupta,
Foivos Karakostas, Dimitri Komatitsch, Qinya Liu, Geordie McBain, Ryan Modrak, Vadim Monteiller, Masaru Nagaso, Elif Oral,
Daniel Peter, Elliott Sales de Andrade,  James Smith, Carl Tape, Eduardo Valero Cano, Huihui Weng, Zhinan Xie:
various code improvements (fault solver, FK/DSM/AxiSEM coupling, gravity perturbations, energy integrals);
inverse problem module; parallel heuristic mesh decomposer; ADIOS2 file I/O support;
ASDF seismogram output; HIP GPU support.\newline

### 2023-06-02 doc/USER_MANUAL/notes_and_acknowledgement.tex

OpenDX \urlwithparentheses{http://www.opendx.org} is open-source
based on IBM Data Explorer, AVS \urlwithparentheses{http://www.avs.com}
is a trademark of Advanced Visualization Systems, and ParaView \urlwithparentheses{http://www.paraview.org}
is an open-source visualization platform.\newline

>>>>

\href{http://www.opendx.org}{OpenDX} is open-source
based on IBM Data Explorer, \href{http://www.avs.com}{AVS}
is a trademark of Advanced Visualization Systems, and \href{http://www.paraview.org}{ParaView}
is an open-source visualization platform.\newline
